---
title: "p8105_hw4_kk3225"
author: "Kwangmin Kim"
date: "October 26, 2017"
output: 
  html_document:
    theme: cosmo
    highlight: haddock
    toc: true
    toc_float:
      collapse: true
      smooth_scroll: false
editor_options: 
  chunk_output_type: console
---

```{r}
library(tidyverse)
library(dplyr)
library(janitor)
library(ggridges)
library(lubridate)
library(forcats)
options(tibble.print_min = 8)
```

### Problem 1
I worked with Parsons, Faith for problem 1. As a lead, I made the raw data tidy.
```{r}
pups_data = read_csv("./data/FAS_pups.csv", col_types= "ciiiii")%>%
  clean_names()%>%
  gather(key = pd_outcome, value = post_natal_day, pd_ears:pd_walk)%>%
  separate(pd_outcome, into = c("pd", "outcome"), sep = "_")%>%
  select(-pd)%>%
  filter(!is.na(post_natal_day))%>%
  arrange(litter_number)

```

### Pups' developmental landmarks

```{r visualize_pups}

pups_data %>%
  # Relevel manually (based on mean postnatal_days)
  mutate(outcome = fct_relevel(outcome, c("ears", "pivot", "walk", "eyes"))) %>%
  ggplot(aes(x = outcome, y = post_natal_day)) +
    geom_boxplot() +
    geom_point(position = "jitter", alpha = .10, color = "blue") +
    labs (x = "Developmental landmark",
          y = "Postnatal days") +
    theme_classic()

```

The boxplot above shows that, among the developmental landmarks, the ears are the first to develop (mean = `r round(pups_data %>% filter(outcome == "ears") %>% pull(post_natal_day) %>% mean(), 1)` days, SD = `r round(pups_data %>% filter(outcome == "ears") %>% pull(post_natal_day) %>% sd(), 1)`), followed by pivoting (mean = `r round(pups_data %>% filter(outcome == "pivot") %>% pull(post_natal_day) %>% mean(), 1)` days, SD = `r round(pups_data %>% filter(outcome == "pivot") %>% pull(post_natal_day) %>% sd(), 1)`), then walking (mean = `r round(pups_data %>% filter(outcome == "walk") %>% pull(post_natal_day) %>% mean(), 1)` days, SD = `r round(pups_data %>% filter(outcome == "walk") %>% pull(post_natal_day) %>% sd(), 1)`), and lastly, the eyes (mean = `r round(pups_data %>% filter(outcome == "eyes") %>% pull(post_natal_day) %>% mean(), 1)` days, SD = `r round(pups_data %>% filter(outcome == "eyes") %>% pull(post_natal_day) %>% sd(), 1)`)
